---
title: "exposure_outcome_updated"
author: "Melissa Tobin"
date: "11/06/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

OS <- Sys.info()
if (OS["sysname"] == "Windows") {
  path <-
    "Z:/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis Results/INTERACT thesis Analysis"
} else {
  path <-
    "/Volumes/hkr-storage/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis Results/INTERACT thesis Analysis"
}
setwd(path)
```

## Loading Packages
```{r}
library(lmtest)
library(tidyverse)
library(ggplot2)
library(haven)
library(janitor)
library(pastecs)
library(psych)
library(car)
library(Hmisc)
library(ggm)
library(polycor)
library(tableone)
library(forcats)
library(gmodels)
library(QuantPsyc)
library(KernSmooth)
library(raster)
library(sp)
library(sf)
library(lubridate)
library(anytime)
library(stringr)
library(stringi)
```

## Reading in Data to make sure timestamps code was right
```{r}
wear_time_stamps_updated_final <- read_csv("wear_time_stamps_updated_final.csv")
wear_time_stamps <- read_csv("wear_time_stamps.csv")
wear_time_stamps_updated <- read_csv("wear_time_stamps_updated.csv")
##everything looks great

colnames(wear_time_stamps_updated_final)[colnames(wear_time_stamps_updated_final)== "interact_id.y"] <- "interact_id"
```

## Total hours, number of days and average hours 
```{r}
wear_time_stamps_updated_final <- wear_time_stamps_updated_final %>% group_by(interact_id) %>% mutate(total_hours = sum(unique_hours))

wear_time_stamps_updated_final <- wear_time_stamps_updated_final %>% group_by(interact_id) %>% mutate(number_days = sum(unique_days))

wear_time_stamps_updated_final <- wear_time_stamps_updated_final %>% group_by(interact_id) %>% mutate(average_hours = total_hours/number_days)

summary_wear_stamps  <- dplyr::select(wear_time_stamps_updated_final, "interact_id", "total_hours", "number_days", "average_hours") #creating a new data frame with just this info

summary_wear_stamps <- summary_wear_stamps %>% distinct(interact_id, .keep_all = TRUE) #removes duplicates

write_csv(summary_wear_stamps, "summary_wear_stamps.csv")
```

## Wear time plots 
```{r}
histo_gps_points_updated <- ggplot(wear_time_stamps_updated_final) + 
                      geom_histogram(aes(unique_seconds)) + 
                      geom_vline(xintercept=7500)
plot(histo_gps_points_updated)

##plot is correct. No GPS days under 7500
```

## Reading in other data
```{r}
gps_join_all_percent_updated <- read_csv("gps_join_all_percent_updated.csv")
victoria_gps_only <- read_csv("victoria_gps_only.csv")
sd_days <- read_csv("all_sds_victoria_phase_1.csv")
```

## Rename INTERACT ID to GPS ID
```{r}
colnames(gps_join_all_percent_updated)[colnames(gps_join_all_percent_updated)== "interact_id.y"] <- "interact_id" #changing to interact_id to help make joining easier later
gps_join_all_percent_updated[is.na(gps_join_all_percent_updated <- gps_join_all_percent_updated)] <- 0 #converted NA's to zero to make merging easier. 

colnames(gps_join_all_percent_updated)[colnames(gps_join_all_percent_updated)== "n.x"] <- "total_points" 

colnames(gps_join_all_percent_updated)[colnames(gps_join_all_percent_updated)== "n.y"] <- "exposure_points" 
```

## Merge gps_join_all_percent_updated with victoria_gps_only 
```{r}
gps_join_all_percent_updated[, "interact_id"] <- apply(gps_join_all_percent_updated[, "interact_id"], 1, function(x) as.integer(x))
victoria_gps_only[, "interact_id"] <- apply(victoria_gps_only[, "interact_id"], 1, function(x) as.integer(x))
#converting to integar first so both interact_id are using the same data format

victoria_gps_only_merged <- left_join(victoria_gps_only, gps_join_all_percent_updated, by = "interact_id") #successfully merged 
```

##Filtering for participants who GPS data isn't valid
```{r}
victoria_gps_only_merged_updated <- victoria_gps_only_merged %>% filter(total_points >= 0)

write_csv(victoria_gps_only_merged_updated, "victoria_gps_only_merged_updated.csv")
```

## Connect PA total and cycling PA with exposure data
```{r}
PA_total_and_cycling <- dplyr::select(victoria_gps_only_merged_updated, "interact_id", "Cycling_formula", "total_pa_met_formula", "proportion_PA", "total_points", "exposure_points", "amount", "percent")

write_csv(PA_total_and_cycling, "PA_total_and_cycling.csv")
```

##Plotting exposure 
```{r}
exposure_plot <- ggplot(PA_total_and_cycling) + 
                      geom_histogram(aes(percent), binwidth = 2)
                
plot(exposure_plot)

tabyl(PA_total_and_cycling$percent)
```

```{r}
Pa_total_plot <- ggplot(PA_total_and_cycling) + 
                      geom_histogram(aes(total_pa_met_formula))
                
plot(Pa_total_plot)

cycling_plot <- ggplot(PA_total_and_cycling) + 
                      geom_histogram(aes(Cycling_formula))
                
plot(cycling_plot)
```

