---
title: "exposure_outcome_updated"
author: "Melissa Tobin"
date: "11/06/2019"
output:   
  html_document:
        keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics = FALSE, ind = 1)

OS <- Sys.info()
if (OS["sysname"] == "Windows") {
  path <-
    "Z:/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis Results/INTERACT thesis Analysis"
} else {
  path <-
    "/Volumes/hkr-storage/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis Results/INTERACT thesis Analysis"
}
setwd(path)
```

## Loading Packages
```{r}
library(lmtest)
library(tidyverse)
library(ggplot2)
library(haven)
library(janitor)
library(pastecs)
library(psych)
library(car)
library(Hmisc)
library(ggm)
library(polycor)
library(tableone)
library(forcats)
library(gmodels)
library(QuantPsyc)
library(KernSmooth)
library(raster)
library(sp)
library(sf)
library(lubridate)
library(anytime)
library(stringr)
library(stringi)
library(finalfit)
library(data.table)
```

## Reading in Data to make sure timestamps code was right
```{r}
wear_time_stamps_updated_final <- read_csv("wear_time_stamps_updated_final.csv")
#wear_time_stamps <- read_csv("wear_time_stamps.csv")
#wear_time_stamps_updated <- read_csv("wear_time_stamps_updated.csv")
##everything looks great

colnames(wear_time_stamps_updated_final)[colnames(wear_time_stamps_updated_final)== "interact_id.y"] <- "interact_id"
```

## Reading in other data
```{r}
gps_join_all_percent_updated <- read_csv("gps_join_all_percent_updated.csv")
victoria_gps_only <- read_csv("victoria_gps_only.csv")
sd_days <- read_csv("all_sds_victoria_phase_1.csv")
weather_data <- read_csv("weather_data_1.csv")
doy_start_end_filtered <- read_csv("doy_start_end_filtered.csv")
```

## Total hours, number of days and average hours 
```{r}
wear_time_stamps_updated_final <- wear_time_stamps_updated_final %>% group_by(interact_id) %>% mutate(total_hours = sum(unique_hours))

wear_time_stamps_updated_final <- wear_time_stamps_updated_final %>% group_by(interact_id) %>% mutate(number_days = sum(unique_days))

wear_time_stamps_updated_final <- wear_time_stamps_updated_final %>% group_by(interact_id) %>% mutate(average_hours = total_hours/number_days)
```

## Weather data
```{r}
weather_data_updated <- weather_data %>% dplyr::select("Date/Time", "Year", "Month", "Day", "Mean Temp", "Total Precip (mm)")

weather_data_updated <- weather_data_updated %>% mutate(doy = lubridate::yday(`Date/Time`))

colnames(weather_data_updated)[colnames(weather_data_updated)== "Mean Temp"] <- "mean_temp"
colnames(weather_data_updated)[colnames(weather_data_updated)== "Total Precip (mm)"] <- "total_precip"

weather_time_stamps_1 <- left_join(wear_time_stamps_updated_final, weather_data_updated, by = "doy")

weather_time_stamps_2 <- weather_time_stamps_1 %>% group_by(interact_id) %>%
  mutate(mean_temp_date = mean(mean_temp, na.rm = TRUE),
           total_precip_date = sum(total_precip, na.rm = TRUE))

summary_wear_stamps  <- dplyr::select(weather_time_stamps_2, "interact_id", "total_hours", "number_days", "average_hours", "mean_temp_date", "total_precip_date") #creating a new data frame with just this info. Includes wear stamps and weather data

summary_wear_stamps <- summary_wear_stamps %>% distinct(interact_id, .keep_all = TRUE) #removes duplicates

write_csv(summary_wear_stamps, "summary_wear_stamps.csv")
```

## Wear time plots 
```{r}
histo_gps_points_updated <- ggplot(wear_time_stamps_updated_final) + 
                      geom_histogram(aes(unique_seconds)) + 
                      geom_vline(xintercept=7500)
plot(histo_gps_points_updated)

##plot is correct. No GPS days under 7500
```


## Renaming columns in exposure file and filtering for NA
```{r}
colnames(gps_join_all_percent_updated)[colnames(gps_join_all_percent_updated)== "interact_id.y"] <- "interact_id" #changing to interact_id to help make joining easier later
gps_join_all_percent_updated[is.na(gps_join_all_percent_updated <- gps_join_all_percent_updated)] <- 0 #converted NA's to zero to make merging easier. 

colnames(gps_join_all_percent_updated)[colnames(gps_join_all_percent_updated)== "n.x"] <- "total_points" 

colnames(gps_join_all_percent_updated)[colnames(gps_join_all_percent_updated)== "n.y"] <- "exposure_points" 
```

## Merge gps_join_all_percent_updated with victoria_gps_only 
```{r}
gps_join_all_percent_updated[, "interact_id"] <- apply(gps_join_all_percent_updated[, "interact_id"], 1, function(x) as.integer(x))
victoria_gps_only[, "interact_id"] <- apply(victoria_gps_only[, "interact_id"], 1, function(x) as.integer(x))
#converting to integar first so both interact_id are using the same data format

victoria_gps_only_merged <- left_join(victoria_gps_only, gps_join_all_percent_updated, by = "interact_id") #successfully merged 
```

## Recoding PA total and cycling PA for outlier 
```{r}
victoria_gps_only_merged$total_pa_met_formula[victoria_gps_only_merged$total_pa_met_formula == 29622.0] <- 22309
tabyl(victoria_gps_only_merged$Cycling_formula)
victoria_gps_only_merged$Cycling_formula[victoria_gps_only_merged$Cycling_formula == 10080] <- 7561
```

##Filtering for participants who GPS data isn't valid
```{r}
victoria_gps_only_merged_updated <- victoria_gps_only_merged %>% filter(total_points >= 0)

write_csv(victoria_gps_only_merged_updated, "victoria_gps_only_merged_updated.csv")
```

## Connect PA total and cycling PA with exposure data
```{r}
PA_total_and_cycling <- dplyr::select(victoria_gps_only_merged_updated, "interact_id", "Cycling_formula", "total_pa_met_formula", "proportion_PA", "total_points", "exposure_points", "amount", "percent")

write_csv(PA_total_and_cycling, "PA_total_and_cycling.csv")
```

## Filtering for file with just SD Days 
```{r}
doy_start_end_final <- doy_start_end_filtered %>% dplyr::select("interact_id", "gps_id", "doy_start", "doy_end")

victoria_gps_only_merged_updated_1 <- left_join(victoria_gps_only_merged_updated, doy_start_end_final, by = "interact_id")
write_csv(victoria_gps_only_merged_updated_1, "victoria_gps_only_merged_updated_1.csv")
```

## Reducing Data frame into a more manageable file
```{r}
victoria_small <- victoria_gps_only_merged_updated_1 %>% dplyr::select("interact_id", "sensedoc_ID", "ethica_ID", "gps_id.x", "residence_cp", "age_calculated", "age_categories", "gender", "health_status", "marital", "income_1", "income_2", "income_satisfy", "ethnicity", "born_canada", "children_1", "car_access", "transp_bikes_adults", "bike_safety",  "bike_freq_a", "bike_freq_b", "bike_freq_c", "bike_freq_d", "path_comf", "residential_street_comf", "res_street_traffic_calming_comf", "major_street_no_bike_lane", "major_street_bike_lane", "major_street_separated_bike_lane", "aaa_familiarity_1", "aaa_idea_1", "aaa_bike_more_1", "Cycling_formula", "total_pa_met_formula", "proportion_PA", "total_points", "exposure_points", "amount", "percent", "doy_start", "doy_end")

write_csv(victoria_small, "victoria_small.csv")

##merging summary time stamps with victoria small

victoria_small_merged <- left_join(victoria_small, summary_wear_stamps, by = "interact_id")

write_csv(victoria_small_merged, "victoria_small_merged.csv")
```

## Recoding and ordering variables for regression 
```{r}
victoria_small_merged <- victoria_small_merged %>% mutate(ethnicity_updated = case_when(
  ethnicity == "Caucasian" ~ "Caucasian",
  ethnicity == "Aboriginal" ~ "Racialized Group",
  ethnicity == "Asian" ~ "Racialized Group",
 ethnicity == "Latin American" ~ "Racialized Group",
  ethnicity == "Unknown" ~ "Racialized Group",
))

victoria_small_merged$income_2 <- factor(victoria_small_merged$income_2, c("$49,000 or less", "$50,000 to $99,999", "$100,000 to $149,999", "$150,000 or more", "I don't know/Prefer not to answer")) 

victoria_small_merged <- victoria_small_merged %>% mutate(gender_updated = case_when(
  gender == "Women" ~ "Women",
  gender == "Men" ~ "Men"
)) 
tabyl(victoria_small_merged$gender_updated)

victoria_small_merged <- victoria_small_merged %>% mutate (gender_check = case_when(
  gender == "Women" ~ 1,
  gender == "Men" ~ 1
))

victoria_small_merged_1 <- filter(victoria_small_merged, gender_check == 1) 

write_csv(victoria_small_merged_1, "victoria_small_merged_1.csv")
```

##Plotting exposure 
```{r}
victoria_small_merged_1 <- read_csv("victoria_small_merged_1.csv")

exposure_plot <- ggplot(victoria_small_merged_1) + 
                      geom_histogram(aes(percent), bins =80) +
  labs(title = "Exposure to the Pandora Protected Cycling Lane",
       x = "Percent Exposure",
       y = "Number of Participants (n)")
                
plot(exposure_plot)

summary(victoria_small_merged_1$percent)
sd(victoria_small_merged_1$percent)
describeBy(victoria_small_merged_1$percent)
```


## Filtering exposure data for outliers (>40%)
```{r}
victoria_exposure_filtered <- victoria_small_merged_1 %>% dplyr::filter(percent <= 40)
tabyl(victoria_exposure_filtered$percent)

exposure_filtered_plot <- ggplot(victoria_exposure_filtered) + 
                      geom_histogram(aes(percent), bins =80) +
  labs(title = "Exposure to the Pandora Protected Cycling Lane",
       x = "Percent Exposure",
       y = "Number of Participants (n)")

plot(exposure_filtered_plot)
```

## Self-report PA stats
```{r}
summary(victoria_small_merged_1$total_pa_met_formula)
sd(victoria_small_merged_1$total_pa_met_formula)
describeBy(victoria_small_merged_1$total_pa_met_formula)
```

## Plotting outcome 
```{r}
pa_total_plot <- ggplot(victoria_small_merged_1) + 
                      geom_histogram(aes(total_pa_met_formula), bins = 80) +
  labs(title = "Total MET-minutes of Physical Activity",
       x = "Total MET-minutes of PA",
       y = "Number of Participants (n)")
                
plot(pa_total_plot)

cycling_plot <- ggplot(PA_total_and_cycling) + 
                      geom_histogram(aes(Cycling_formula))
                
plot(cycling_plot)
```

## GPS Wear Time 
```{r}
summary(victoria_small_merged_1$total_hours)
sd(victoria_small_merged_1$total_hours)

summary(victoria_small_merged_1$number_days)
sd(victoria_small_merged_1$number_days)

summary(victoria_small_merged_1$average_hours)
sd(victoria_small_merged_1$average_hours)
```

## Filtering accelerometer data
```{r}
power_victoria_merged_filtered <- read_csv("power_victoria_merged_filtered.csv")
table(power_victoria_merged_filtered$summary_count)

power_victoria_accel_filtered <- power_victoria_merged_filtered %>% filter(summary_count <= 10000)

write_csv(power_victoria_accel_filtered, "power_victoria_accel_filtered.csv")
summary(power_victoria_accel_filtered$summary_count)
sd(power_victoria_accel_filtered$summary_count)
describeBy(power_victoria_accel_filtered$summary_count)
```

## Filtering accelerometer data for filtered exposure data
```{r}
power_victoria_accel_filtered <- fread("power_victoria_accel_filtered.csv")

power_victoria_filtered <- power_victoria_accel_filtered %>% dplyr::filter(percent <= 40)
```

## Plotting Accelerometer data
```{r}
accel_plot <- ggplot(power_victoria_accel_filtered) + 
                      geom_histogram(aes(summary_count), bins = 15) +
  labs(title = "Accelerometer Activity Counts",
       x = "Activity Count",
       y = "Number of Counts (n)")
                
plot(accel_plot)
```

## Making figure for preference for AT infrastructure
```{r}
victoria_merged_filter <- read_csv("victoria_merged_filter.csv")

victoria_merged_filter$path_comf <- factor(victoria_merged_filter$path_comf, c("Very uncomfortable", "Somewhat comfortable", "Very comfortable"))

path_comfortable_plot <- ggplot (data = victoria_merged_filter, aes(path_comf)) +
    geom_bar(aes()) + 
      labs(title = "Preference for Bicycle Paths", 
          x = "Level of Preference", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=45, hjust=1))

plot(path_comfortable_plot)

```

```{r}
victoria_merged_filter <- read_csv("victoria_merged_filter.csv")

at_infrastructure <- victoria_merged_filter %>% dplyr::select(path_comf, residential_street_comf, res_street_traffic_calming_comf, major_street_no_bike_lane, major_street_bike_lane, major_street_separated_bike_lane)
```

## Separated Path
```{r}
typeof(at_infrastructure$path_comf)  
at_infrastructure$path_comf <- as.character(at_infrastructure$path_comf)

colnames(at_infrastructure)[colnames(at_infrastructure) == "path_comf"] <- "1_separated_path"

at_infrastructure$`1_separated_path` <- as.character(at_infrastructure$`1_separated_path`)

ggplot(at_infrastructure) +
  geom_bar(aes(x = `1_separated_path`))

at_infrastructure <- at_infrastructure %>% mutate(`1_separated_path` = case_when(
  `1_separated_path` == "Very uncomfortable" ~ "1_very_uncomfortable",
  `1_separated_path` == "Somewhat uncomfortable" ~ "2_somewhat_uncomfortable",
  `1_separated_path` == "Somewhat comfortable" ~ "3_somewhat_comfortable", 
  `1_separated_path` == "Very comfortable" ~ "4_very_comfortable"
)) 
```

## Residential street
```{r}
at_infrastructure$residential_street_comf <- as.character(at_infrastructure$residential_street_comf)

colnames(at_infrastructure)[colnames(at_infrastructure) == "residential_street_comf"] <- "2_residential_street"

at_infrastructure <- at_infrastructure %>% mutate(`2_residential_street` = case_when(
  `2_residential_street` == "Very uncomfortable" ~ "1_very_uncomfortable",
  `2_residential_street` == "Somewhat uncomfortable" ~ "2_somewhat_uncomfortable",
  `2_residential_street` == "Somewhat comfortable" ~ "3_somewhat_comfortable", 
  `2_residential_street` == "Very comfortable" ~ "4_very_comfortable"
)) 
```

## Residential Street Traffic calming
```{r}
at_infrastructure$res_street_traffic_calming_comf <- as.character(at_infrastructure$res_street_traffic_calming_comf)

colnames(at_infrastructure)[colnames(at_infrastructure) == "res_street_traffic_calming_comf"] <- "3_residential_street_traffic_calming"

at_infrastructure <- at_infrastructure %>% mutate(`3_residential_street_traffic_calming` = case_when(
  `3_residential_street_traffic_calming` == "Very uncomfortable" ~ "1_very_uncomfortable",
  `3_residential_street_traffic_calming` == "Somewhat uncomfortable" ~ "2_somewhat_uncomfortable",
  `3_residential_street_traffic_calming` == "Somewhat comfortable" ~ "3_somewhat_comfortable", 
  `3_residential_street_traffic_calming` == "Very comfortable" ~ "4_very_comfortable",
   `3_residential_street_traffic_calming` == "I don't know/Prefer not to answer" ~ "5_Unsure/Prefer_not_to_answer"
)) 
```

## Major street no bike lane 
```{r}
at_infrastructure$major_street_no_bike_lane <- as.character(at_infrastructure$major_street_no_bike_lane)

colnames(at_infrastructure)[colnames(at_infrastructure) == "major_street_no_bike_lane"] <- "4_major_street_no_bike_lane"

at_infrastructure <- at_infrastructure %>% mutate(`4_major_street_no_bike_lane` = case_when(
 `4_major_street_no_bike_lane` == "Very uncomfortable" ~ "1_very_uncomfortable",
  `4_major_street_no_bike_lane` == "Somewhat uncomfortable" ~ "2_somewhat_uncomfortable",
  `4_major_street_no_bike_lane` == "Somewhat comfortable" ~ "3_somewhat_comfortable", 
  `4_major_street_no_bike_lane` == "Very comfortable" ~ "4_very_comfortable"
)) 
```

## Major street bike lane
```{r}
at_infrastructure$major_street_bike_lane <- as.character(at_infrastructure$major_street_bike_lane)

colnames(at_infrastructure)[colnames(at_infrastructure) == "major_street_bike_lane"] <- "5_major_street_bike_lane"

at_infrastructure <- at_infrastructure %>% mutate(`5_major_street_bike_lane` = case_when(
 `5_major_street_bike_lane` == "Very uncomfortable" ~ "1_very_uncomfortable",
  `5_major_street_bike_lane` == "Somewhat uncomfortable" ~ "2_somewhat_uncomfortable",
  `5_major_street_bike_lane` == "Somewhat comfortable" ~ "3_somewhat_comfortable", 
  `5_major_street_bike_lane` == "Very comfortable" ~ "4_very_comfortable"
)) 
```

## Major street separated bike lane
```{r}
at_infrastructure$major_street_separated_bike_lane <- as.character(at_infrastructure$major_street_separated_bike_lane)

colnames(at_infrastructure)[colnames(at_infrastructure) == "major_street_separated_bike_lane"] <- "6_major_street_separated_bike_lane"

at_infrastructure <- at_infrastructure %>% mutate(`6_major_street_separated_bike_lane` = case_when(
 `6_major_street_separated_bike_lane` == "Very uncomfortable" ~ "1_very_uncomfortable",
  `6_major_street_separated_bike_lane` == "Somewhat uncomfortable" ~ "2_somewhat_uncomfortable",
 `6_major_street_separated_bike_lane` == "Somewhat comfortable" ~ "3_somewhat_comfortable", 
 `6_major_street_separated_bike_lane` == "Very comfortable" ~ "4_very_comfortable",
   `6_major_street_separated_bike_lane` == "I don't know/Prefer not to answer" ~ "5_Unsure/Prefer_not_to_answer"
)) 
```

## Graph with all 6 AT Types
```{r}
at_infrastructure %>%
  keep(is.character) %>% 
  gather() %>% 
  ggplot(aes(value)) +
    facet_wrap(~ key, scales = "free") +
    geom_bar() + theme(axis.text.x = element_text(angle=45, hjust=1)) + 
      labs(title = "Preference for Different Types of Active Transportation Infrastructure", 
          x = "Level of Preference", 
          y = "Number of Participants (n)") 
```

