---
title: "exposure_outcome_updated"
author: "Melissa Tobin"
date: "11/06/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics = FALSE, ind = 1)

OS <- Sys.info()
if (OS["sysname"] == "Windows") {
  path <-
    "Z:/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis Results/INTERACT thesis Analysis"
} else {
  path <-
    "/Volumes/hkr-storage/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis Results/INTERACT thesis Analysis"
}
setwd(path)
```

## Loading Packages
```{r}
library(lmtest)
library(tidyverse)
library(ggplot2)
library(haven)
library(janitor)
library(pastecs)
library(psych)
library(car)
library(Hmisc)
library(ggm)
library(polycor)
library(tableone)
library(forcats)
library(gmodels)
library(QuantPsyc)
library(KernSmooth)
library(raster)
library(sp)
library(sf)
library(lubridate)
library(anytime)
library(stringr)
library(stringi)
library(finalfit)
```

## Reading in Data to make sure timestamps code was right
```{r}
wear_time_stamps_updated_final <- read_csv("wear_time_stamps_updated_final.csv")
wear_time_stamps <- read_csv("wear_time_stamps.csv")
wear_time_stamps_updated <- read_csv("wear_time_stamps_updated.csv")
##everything looks great

colnames(wear_time_stamps_updated_final)[colnames(wear_time_stamps_updated_final)== "interact_id.y"] <- "interact_id"
```

## Reading in other data
```{r}
gps_join_all_percent_updated <- read_csv("gps_join_all_percent_updated.csv")
victoria_gps_only <- read_csv("victoria_gps_only.csv")
sd_days <- read_csv("all_sds_victoria_phase_1.csv")
weather_data <- read_csv("weather_data_1.csv")
doy_start_end_filtered <- read_csv("doy_start_end_filtered.csv")
```


## Total hours, number of days and average hours 
```{r}
wear_time_stamps_updated_final <- wear_time_stamps_updated_final %>% group_by(interact_id) %>% mutate(total_hours = sum(unique_hours))

wear_time_stamps_updated_final <- wear_time_stamps_updated_final %>% group_by(interact_id) %>% mutate(number_days = sum(unique_days))

wear_time_stamps_updated_final <- wear_time_stamps_updated_final %>% group_by(interact_id) %>% mutate(average_hours = total_hours/number_days)
```

## Weather data
```{r}
weather_data_updated <- weather_data %>% dplyr::select("Date/Time", "Year", "Month", "Day", "Mean Temp", "Total Precip (mm)")

weather_data_updated <- weather_data_updated %>% mutate(doy = lubridate::yday(`Date/Time`))

colnames(weather_data_updated)[colnames(weather_data_updated)== "Mean Temp"] <- "mean_temp"
colnames(weather_data_updated)[colnames(weather_data_updated)== "Total Precip (mm)"] <- "total_precip"

weather_time_stamps_1 <- left_join(wear_time_stamps_updated_final, weather_data_updated, by = "doy")

weather_time_stamps_2 <- weather_time_stamps_1 %>% group_by(interact_id) %>%
  mutate(mean_temp_date = mean(mean_temp, na.rm = TRUE),
           total_precip_date = sum(total_precip, na.rm = TRUE))

summary_wear_stamps  <- dplyr::select(weather_time_stamps_2, "interact_id", "total_hours", "number_days", "average_hours", "mean_temp_date", "total_precip_date") #creating a new data frame with just this info. Includes wear stamps and weather data

summary_wear_stamps <- summary_wear_stamps %>% distinct(interact_id, .keep_all = TRUE) #removes duplicates

write_csv(summary_wear_stamps, "summary_wear_stamps.csv")
```

## Wear time plots 
```{r}
histo_gps_points_updated <- ggplot(wear_time_stamps_updated_final) + 
                      geom_histogram(aes(unique_seconds)) + 
                      geom_vline(xintercept=7500)
plot(histo_gps_points_updated)

##plot is correct. No GPS days under 7500
```


## Renaming columns in exposure file and filtering for NA
```{r}
colnames(gps_join_all_percent_updated)[colnames(gps_join_all_percent_updated)== "interact_id.y"] <- "interact_id" #changing to interact_id to help make joining easier later
gps_join_all_percent_updated[is.na(gps_join_all_percent_updated <- gps_join_all_percent_updated)] <- 0 #converted NA's to zero to make merging easier. 

colnames(gps_join_all_percent_updated)[colnames(gps_join_all_percent_updated)== "n.x"] <- "total_points" 

colnames(gps_join_all_percent_updated)[colnames(gps_join_all_percent_updated)== "n.y"] <- "exposure_points" 
```

## Merge gps_join_all_percent_updated with victoria_gps_only 
```{r}
gps_join_all_percent_updated[, "interact_id"] <- apply(gps_join_all_percent_updated[, "interact_id"], 1, function(x) as.integer(x))
victoria_gps_only[, "interact_id"] <- apply(victoria_gps_only[, "interact_id"], 1, function(x) as.integer(x))
#converting to integar first so both interact_id are using the same data format

victoria_gps_only_merged <- left_join(victoria_gps_only, gps_join_all_percent_updated, by = "interact_id") #successfully merged 
```

## Recoding PA total and cycling PA for outlier 
```{r}
victoria_gps_only_merged$total_pa_met_formula[victoria_gps_only_merged$total_pa_met_formula == 29622.0] <- 22309
tabyl(victoria_gps_only_merged$Cycling_formula)
victoria_gps_only_merged$Cycling_formula[victoria_gps_only_merged$Cycling_formula == 10080] <- 7561
```

##Filtering for participants who GPS data isn't valid
```{r}
victoria_gps_only_merged_updated <- victoria_gps_only_merged %>% filter(total_points >= 0)

write_csv(victoria_gps_only_merged_updated, "victoria_gps_only_merged_updated.csv")
```

## Connect PA total and cycling PA with exposure data
```{r}
PA_total_and_cycling <- dplyr::select(victoria_gps_only_merged_updated, "interact_id", "Cycling_formula", "total_pa_met_formula", "proportion_PA", "total_points", "exposure_points", "amount", "percent")

write_csv(PA_total_and_cycling, "PA_total_and_cycling.csv")
```

##Plotting exposure 
```{r}
exposure_plot <- ggplot(PA_total_and_cycling) + 
                      geom_histogram(aes(percent), binwidth = 2)
                
plot(exposure_plot)

tabyl(PA_total_and_cycling$percent)
```

## Plotting outcome 
```{r}
pa_total_plot <- ggplot(PA_total_and_cycling) + 
                      geom_histogram(aes(total_pa_met_formula))
                
plot(pa_total_plot)

cycling_plot <- ggplot(PA_total_and_cycling) + 
                      geom_histogram(aes(Cycling_formula))
                
plot(cycling_plot)
```

## Filtering for file with just SD Days 
```{r}
doy_start_end_final <- doy_start_end_filtered %>% dplyr::select("interact_id", "gps_id", "doy_start", "doy_end")

victoria_gps_only_merged_updated_1 <- left_join(victoria_gps_only_merged_updated, doy_start_end_final, by = "interact_id")
write_csv(victoria_gps_only_merged_updated_1, "victoria_gps_only_merged_updated_1.csv")
```


## Reducing Data frame into a more manageable file
```{r}
victoria_small <- victoria_gps_only_merged_updated_1 %>% dplyr::select("interact_id", "sensedoc_ID", "ethica_ID", "gps_id.x", "residence_cp", "age_calculated", "age_categories", "gender", "health_status", "marital", "income_1", "income_2", "income_satisfy", "ethnicity", "born_canada", "children_1", "car_access", "transp_bikes_adults", "bike_safety",  "bike_freq_a", "bike_freq_b", "bike_freq_c", "bike_freq_d", "path_comf", "residential_street_comf", "res_street_traffic_calming_comf", "major_street_no_bike_lane", "major_street_bike_lane", "major_street_separated_bike_lane", "aaa_familiarity_1", "aaa_idea_1", "aaa_bike_more_1", "Cycling_formula", "total_pa_met_formula", "proportion_PA", "total_points", "exposure_points", "amount", "percent", "doy_start", "doy_end")

write_csv(victoria_small, "victoria_small.csv")

##merging summary time stamps with victoria small

victoria_small_merged <- left_join(victoria_small, summary_wear_stamps, by = "interact_id")

write_csv(victoria_small_merged, "victoria_small_merged.csv")
```

## Models
```{r}
regression_1 <- lm(total_pa_met_formula ~ percent, data = victoria_small_merged)

summary(regression_1)
lm.beta(regression_1) ##This isn't working. 
confint(regression_1)
#plot(regression_1)
```

## Trying final fit
```{r}
explanatory = c("percent", "age_categories")
dependent = "total_pa_met_formula"
victoria_small_merged %>% finalfit(dependent, explanatory)
knitr::kable(t1, row.names = FALSE, align = c("l", "l", "r", "r", "r")) #not sure what this does but copied anyways from the explanation 
typeof(victoria_small_merged$income_2)

typeof(victoria_small_merged$gender)
typeof(victoria_small_merged$age_categories)
tabyl(victoria_small_merged$age_categories)
```

