---
title: "gps_participant_survey_analysis"
author: "Melissa Tobin"
date: "31/05/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

OS <- Sys.info()
if (OS["sysname"] == "Windows") {
  path <-
    "Z:/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis Results/INTERACT thesis Analysis"
} else {
  path <-
    "/Volumes/hkr-storage/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis Results/INTERACT thesis Analysis"
}
setwd(path)
```

## Loading Packages
```{r}
install.packages("lmtest")
library(lmtest)
library(tidyverse)
library(ggplot2)
library(haven)
library(janitor)
library(pastecs)
library(psych)
library(car)
library(Hmisc)
library(ggm)
library(polycor)
library(tableone)
library(forcats)
library(gmodels)
library(QuantPsyc)
library(KernSmooth)
library(raster)
library(sp)
library(sf)
```

## Loading in Data
```{r}
victoria_small_merged <- read_csv("victoria_small_merged.csv")
```


## Age descriptive Statistics for Victoria
```{r}
summary(victoria_small_merged$age_calculated, na.rm = TRUE)

sd(victoria_small_merged$age_calculated)
```

## Age descriptive Statistics for Victoria
```{r}
age_categories_plot <- ggplot (data = victoria_small_merged, aes(age_categories)) + 
    geom_bar() + 
        labs(title = "Age ", 
           x = "Age Categories", 
            y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=60, hjust=1))
plot(age_categories_plot)
```

## Gender
```{r}
tabyl(victoria_small_merged$gender)

gender_plot <- ggplot(data = victoria_new_ID_gps, aes(gender)) +
  geom_bar(aes(fill = gender)) +
  labs(title = "Gender",
       x = "Gender Type",
       y = "Number of Participants (n)")
plot(gender_plot)
```


## Health Status
```{r}
victoria_small_merged$health_status <- factor(victoria_small_merged$health_status, c("Poor", "Fair", "Good", "Very Good", "Excellent"))
tabyl(victoria_small_merged$health_status)

health_plot <- ggplot(data = victoria_gps_only, aes(health_status)) +
  geom_bar() +
  labs(title = "Health Status",
       x = "Health Status",
       y = "Number of Participants (n)") 
plot(health_plot)
```

## Marital Status
```{r}
tabyl(victoria_small_merged$marital)
marital_plot <- ggplot(data = victoria_gps_only, aes(marital)) +
  geom_bar() +
  labs(title = "Marital Status",
       x = "Marital Status",
       y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=60, hjust=1))
plot(marital_plot)
```
## Ethnicity 
```{r}
tabyl(victoria_small_merged$ethnicity)
ethnicity_plot <- ggplot(data = victoria_gps_only, aes(ethnicity)) +
  geom_bar() +
  labs(title = "Ethnicity",
       x = "Ethnic Group",
       y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=60, hjust=1))
plot(ethnicity_plot)
```

## Income
```{r}

victoria_small_merged$income_1 <- factor(victoria_small_merged$income_1, c("No income", "$1 to $9,999", "$10,000 to $14,999", "$15,000 to $19,999", "$20,000 to $29,999", "$30,000 to $39,999", "$40,000 to $49,999","$50,000 to $99,999","$100,000 to $149,999","$150,000 to $199,999", "$200,000 or more", "I don't know/Prefer not to answer"))

tabyl(victoria_small_merged$income_1)


income_plot <- ggplot(data = victoria_new_ID_gps, aes(income_1)) +
  geom_bar() +
  labs(title = "Income",
       x = "Income Level",
       y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=60, hjust=1))
plot(income_plot)

tabyl(victoria_small_merged$income_2)
```

## Children 
```{r}
tabyl(victoria_small_merged$children_1)
```

## Born in Canada
```{r}
tabyl(victoria_small_merged$born_canada)
```

## Car Access
```{r}
tabyl(victoria_small_merged$car_access)

victoria_small_merged <- victoria_small_merged %>% mutate(car_access_1 = case_when(
  car_access == 1 ~ "Yes",
  car_access == 2 ~ "No"
))
tabyl(victoria_small_merged$car_access_1)
tabyl(victoria_gps_only$cars_household)
```

## Support for the AAA
```{r}
tabyl(victoria_small_merged$aaa_familiarity_1)

victoria_small_merged$aaa_idea_1 <- factor(victoria_small_merged$aaa_idea_1, c("I don't know", "Very bad idea", "Somewhat bad idea", "Somewhat good idea", "Very good idea"))
tabyl(victoria_small_merged$aaa_idea_1)
tabyl(victoria_small_merged$aaa_bike_more_1)
```

##Preference for Separated Bike Lane
```{r}
victoria_small_merged$major_street_separated_bike_lane <- factor(victoria_small_merged$major_street_separated_bike_lane, c( "Very uncomfortable", "Somewhat uncomfortable", "Somewhat comfortable", "Very comfortable", "I don't know/Prefer not to answer"))
tabyl(victoria_small_merged$major_street_separated_bike_lane)

tabyl(victoria_small_merged$major_street_separated_bike_lane)
```

## Percieved Cycling Safety in Victoria
```{r}
victoria_small_merged <- victoria_small_merged %>% mutate(bike_safety_1 = case_when(
  bike_safety == 1 ~ "Very safe",
  bike_safety == 2 ~ "Somewhat safe",
  bike_safety == 3 ~ "Neither safe nor unsafe",
  bike_safety == 4 ~ "Somewhat dangerous",
  bike_safety == 5 ~ "Very dangerous",
))
tabyl(victoria_small_merged$bike_safety_1)

victoria_small_merged$bike_safety_1 <- factor(victoria_small_merged$bike_safety_1, c( "Very safe", "Somewhat safe", "Neither safe nor unsafe", "Somewhat dangerous", "Very dangerous"))
tabyl(victoria_small_merged$bike_safety_1)
```

## Bike frequency by season
```{r}

summary(victoria_small_merged$bike_freq_a)
sd(victoria_small_merged$bike_freq_a)

summary(victoria_small_merged$bike_freq_b)
sd(victoria_small_merged$bike_freq_b, na.rm = TRUE)

summary(victoria_small_merged$bike_freq_c)
sd(victoria_small_merged$bike_freq_c)

summary(victoria_small_merged$bike_freq_d)
sd(victoria_small_merged$bike_freq_d, na.rm = TRUE)
```

## Cycing infrastructure preference
```{r}
tabyl(victoria_small_merged$path_comf)
tabyl(victoria_small_merged$residential_street_comf)
tabyl(victoria_small_merged$res_street_traffic_calming_comf)
tabyl(victoria_small_merged$major_street_no_bike_lane)
tabyl(victoria_small_merged$major_street_bike_lane)
```

