---
title: "HKR 6610 - Online Survey Analysis (Gender)"
author: "Melissa Tobin"
date: '2019-05-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Packages
```{r}
library(lmtest)
library(tidyverse)
library(ggplot2)
library(haven)
library(janitor)
library(pastecs)
library(psych)
library(car)
library(Hmisc)
library(ggm)
library(polycor)
library(tableone)
library(forcats)
library(gmodels)
library(QuantPsyc)
```

## Reading in Data
```{r}
getwd()
#setwd("/Volumes/hkr-storage/Research/dfuller/Walkabilly/studies/INTERACT/Data/Health") #only use on lab computer

eligibility <- read_csv("eligibility_1vic_main.90838bb.csv")
health_data <- read_csv("health_1vic_main.90838bb.csv")
van_eligibility <- read_csv("eligibility_1van_main.90838bb.csv")
van_health <- read_csv("health_1van_main.90838bb.csv")

```

## Merging Data together
```{r}
victoria_merged <- full_join(eligibility, health_data, by = "treksoft_id")
vancouver_merged <- full_join(van_eligibility, van_health, by = "treksoft_id")
```

## Merging round two 
```{r}
victoria_merged_filter <- filter(victoria_merged, transp_bikes_adults >= 0)
vancouver_merged_filter <- filter(vancouver_merged, transp_main_mode >= 0)
```

## Separating Birth Date into Year/Month/Day
```{r}
victoria_merged_filter <- separate(victoria_merged_filter, birth_date, c("year", "month", "day"), sep = "-")
vancouver_merged_filter <- separate(vancouver_merged_filter, birth_date, c("year", "month", "day"), sep = "-")
```

## Adding new column for age
```{r}
victoria_merged_filter$year <- as.numeric(victoria_merged_filter$year)
victoria_merged_filter <- mutate(victoria_merged_filter, "age_calculated" = 2017 - year)
vancouver_merged_filter$year <- as.numeric(vancouver_merged_filter$year)
vancouver_merged_filter <- mutate(vancouver_merged_filter, "age_calculated" = 2018 - year)
```

## Age descriptive Statistics for Vancouver
```{r}
summary(vancouver_merged_filter$age_calculated, na.rm = TRUE)

sd(vancouver_merged_filter$age_calculated)
```

## Age descriptive Statistics for Victoria
```{r}
summary(victoria_merged_filter$age_calculated, na.rm = TRUE)
sd(victoria_merged_filter$age_calculated)
```

## Gender and Sex Vancouver
```{r}
tabyl(vancouver_merged_filter$sex)
tabyl(vancouver_merged_filter$gender)
```

## Gender Victoria
```{r}
victoria_merged_filter <- victoria_merged_filter %>% mutate(gender = case_when(
  gender_vic_1.x == 1 & gender_vic_4.x == 1 ~ "LGBTQ+",
  gender_vic_1.x == 1 ~ "Men",
  gender_vic_2.x == 1 ~ "Women", 
  gender_vic_3.x == 1 ~ "LGBTQ+",
  gender_vic_4.x == 1 ~ "LGBTQ+"
)) 

victoria_merged_filter$gender <- factor(victoria_merged_filter$gender, c("Women", "Men", "LGBTQ+")) 
tabyl(victoria_merged_filter$gender)
tabyl(victoria_merged_filter$gender_vic.x)
```

## Age statistics grouped by gender
```{r}
describeBy(victoria_merged_filter$age_calculated, victoria_merged_filter$gender)
```

## Trying a new table 
```{r}
table_age_gender <- table(victoria_merged_filter$age_calculated, victoria_merged_filter$gender)
table_age_gender
margin.table(table_age_gender, 1)
prop.table(table_age_gender)
```

## Plotting Gender

```{r}
gender_plot <- ggplot(data = victoria_merged_filter, aes(gender)) +
  geom_bar(aes(fill = gender)) +
  labs(title = "Gender",
       x = "Gender Type",
       y = "Number of Participants (n)")
plot(gender_plot)
```


## Plotting the gender and age groupings
```{r}
age_grouped_plot <- ggplot (data = victoria_merged_filter, aes(age_calculated)) + 
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Age ", 
          x = "Housing Type", 
          y = "Number of Participants (n)")
plot(age_grouped_plot)
```

## Age Categories (using stats can age groups)
```{r}
victoria_merged_filter <- victoria_merged_filter %>% mutate(age_categories = case_when(
  age_calculated < 25 ~ "20-24",
  age_calculated >= 25 & age_calculated <= 29 ~ "25-29",
  age_calculated >= 30 & age_calculated <= 34 ~ "30-34", 
  age_calculated >= 35 & age_calculated <= 39 ~ "35-39",
  age_calculated >= 40 & age_calculated <= 44 ~ "40-44",
  age_calculated >= 45 & age_calculated <= 49 ~ "45-49",
  age_calculated >= 50 & age_calculated <= 54 ~ "50-54",
  age_calculated >= 55 & age_calculated <= 59 ~ "55-59", 
  age_calculated >= 60 & age_calculated <= 64 ~ "60-64",
  age_calculated >= 65 & age_calculated <= 69 ~ "65-69",
  age_calculated >= 70 & age_calculated <= 74 ~ "70-74", 
  age_calculated >= 75 & age_calculated <= 79 ~ "75-79",
  age_calculated >= 80 & age_calculated <= 84 ~ "80-84"
))
tabyl(victoria_merged_filter$age_categories)
```

## Tables for gender and age categories

```{r}
table(victoria_merged_filter$age_categories, victoria_merged_filter$gender)
CrossTable(victoria_merged_filter$age_categories, victoria_merged_filter$gender)
```

## Plotting the gender and age categories
```{r}
age_categories_plot <- ggplot (data = victoria_merged_filter, aes(age_categories)) + 
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Age ", 
          x = "Age Categories", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=60, hjust=1))
plot(age_categories_plot)
```


## Housing 
```{r}
victoria_merged_filter <- victoria_merged_filter %>% mutate(housing = case_when(
  house_tenure == 1 ~ "Owner",
  house_tenure == 2 ~ "Tenant", 
  house_tenure == 3 ~ "Resident with friends or relatives",
  house_tenure == 4 ~ "Resident not with friends or relatives", 
  house_tenure == 5 ~ "Other"
))

victoria_merged_filter$housing <- factor(victoria_merged_filter$housing, c("Other", "Resident not with friends or relatives", "Resident with friends or relatives", "Tenant", "Owner")) 
tabyl(victoria_merged_filter$housing)
```

## Table for housing and gender
```{r}
table(victoria_merged_filter$housing, victoria_merged_filter$gender)
CrossTable(victoria_merged_filter$housing, victoria_merged_filter$gender)
```

## Housing Graph
```{r}
housing_bar <- ggplot (data = victoria_merged_filter, aes(housing)) + 
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Living Situation ", 
          x = "Living Situation", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=60, hjust=1))
plot(housing_bar)
```


## Dwelling Type 
```{r}
tabyl(victoria_merged_filter$dwelling_type)

victoria_merged_filter <- victoria_merged_filter %>% mutate(housing_type = case_when(
  dwelling_type == 1 ~ "Single-detached house",
  dwelling_type == 2 ~ "Semi-detached house", 
  dwelling_type == 3 ~ "Row house",
  dwelling_type == 4 ~ "Apartment/Condo in a duplex or triplex", 
  dwelling_type == 5 ~ "Apartment/Condo with fewer than 5 storeys",
  dwelling_type == 6 ~ "Apartment/Condo with more than 5 storeys",
  dwelling_type == 7 ~ "Mobile Home",
  dwelling_type == 8 ~ "Seniors Home",
  dwelling_type == 9 ~ "Other"
))

victoria_merged_filter$housing_type <- factor(victoria_merged_filter$housing_type, c("Other", "Seniors Home", "Mobile Home", "Apartment/Condo with more than 5 storeys", "Apartment/Condo with fewer than 5 storeys", "Apartment/Condo in a duplex or triplex", "Row house", "Semi-detached house", "Single-detached house" )) 
tabyl(victoria_merged_filter$housing_type)
```

## Table for housing type and gender
```{r}
table(victoria_merged_filter$housing_type, victoria_merged_filter$gender)
CrossTable(victoria_merged_filter$housing_type, victoria_merged_filter$gender)
```

## Housing Type and Gender Graph
```{r}
housing_type_bar <- ggplot (data = victoria_merged_filter, aes(housing_type)) + 
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Housing ", 
          x = "Housing Type", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=60, hjust=1))
plot(housing_type_bar)
```


## Health Status
```{r}
tabyl(victoria_merged_filter$sf1)

victoria_merged_filter <- victoria_merged_filter %>% mutate(health_status = case_when(
  sf1 == 1 ~ "Excellent",
  sf1 == 2 ~ "Very Good", 
  sf1 == 3 ~ "Good",
  sf1 == 4 ~ "Fair", 
  sf1 == 5 ~ "Poor"
))

victoria_merged_filter$health_status <- factor(victoria_merged_filter$health_status, c("Poor", "Fair", "Good", "Very Good", "Excellent")) #WORKED - puts the graph in order
```

## Trying a new table 
```{r}
table_health_status_gender <- table(victoria_merged_filter$health_status, victoria_merged_filter$gender)
table_health_status_gender
margin.table(table_health_status_gender, 1)
margin.table(table_health_status_gender, 2)
prop.table(table_health_status_gender)
prop.table(table_health_status_gender, 1)
prop.table(table_health_status_gender, 2)

CrossTable(victoria_merged_filter$health_status, victoria_merged_filter$gender)
table(victoria_merged_filter$health_status, victoria_merged_filter$gender)
## cross table and table are good. 
```

## Health Status by gender plot 
```{r}
health_status_plot <- ggplot(data = victoria_merged_filter, aes(health_status)) + 
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Health Status and Gender ", 
          x = "Health Status ", 
          y = "Number of Participants (n)") 

plot(health_status_plot)
```

## Marital Status
```{r}
tabyl(victoria_merged_filter$marital_status)

victoria_merged_filter <- victoria_merged_filter %>% mutate(marital = case_when(
  marital_status == 1 ~ "Single (never married)",
  marital_status == 2 ~ "Married (or common law)", 
  marital_status == 3 ~ "Separated or divorced",
  marital_status == 4 ~ "Widowed"
))
tabyl(victoria_merged_filter$marital)
```

## Table for Marital status and gender
```{r}
table(victoria_merged_filter$marital, victoria_merged_filter$gender)
CrossTable(victoria_merged_filter$marital, victoria_merged_filter$gender)
```

## Marital Status and Gender Plot
```{r}
marital_status_plot <- ggplot (data = victoria_merged_filter, aes(marital)) + 
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Marital Status and Gender ", 
          x = "Marital Status ", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=45, hjust=1))
plot(marital_status_plot)
```

## Children (Yes/No)
```{r}
tabyl(victoria_merged_filter$children)

victoria_merged_filter <- victoria_merged_filter %>% mutate(children_1 = case_when(
  children == 1 ~ "Yes",
  children == 2 ~ "No"
))
tabyl(victoria_merged_filter$children_1)
```

## Children living 
```{r}
tabyl(victoria_merged_filter$living_children)
```

##Children living and gender plot
```{r}
children_living_plot <- ggplot (data = victoria_merged_filter, aes(living_children)) + 
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Children living and Gender ", 
          x = "Children living ", 
          y = "Number of Participants (n)")
plot(children_living_plot)
```

## Children living in household
```{r}
tabyl(victoria_merged_filter$children_household)
```

## Children living in household and Gender Plot
```{r}
children_household_plot <- ggplot (data = victoria_merged_filter, aes(children_household)) + 
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Children living in household and Gender ", 
          x = "Children living in household ", 
          y = "Number of Participants (n)")
plot(children_household_plot)
```

## Born in Canada
```{r}
tabyl(victoria_merged_filter$born_can)

victoria_merged_filter <- victoria_merged_filter %>% mutate(born_canada = case_when(
  born_can == 1 ~ "Yes",
  born_can == 2 ~ "No"
))
tabyl(victoria_merged_filter$born_canada)
```

## Born in Canada and Gender Plot
```{r}
born_canada_plot <- ggplot (data = victoria_merged_filter, aes(born_canada)) + 
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Born in Canada and Gender ", 
          x = "Born in Canada ", 
          y = "Number of Participants (n)")
plot(born_canada_plot)
```

## Ethinic/Cultural Groups
```{r}
tabyl(victoria_merged_filter$group_id)

victoria_merged_filter <- victoria_merged_filter %>% mutate(ethnicity = case_when(
  group_id_1 == 1 & group_id_2 == 1 & group_id_4 == 1 ~ "Aboriginal",
  group_id_1 == 1 & group_id_4 == 1 ~ "Aboriginal",
  group_id_2 == 1 & group_id_4 == 1 ~ "Asian", 
  group_id_4 == 1 & group_id_1 == 1 ~ "Aboriginal",
  group_id_4 == 1 & group_id_6 == 1 ~ "Middle Eastern",
  group_id_2 == 1 ~ "Asian",
  group_id_4 == 1 ~ "Caucasian",
  group_id_5 == 1 ~ "Latin American",
  group_id_77 == 1 ~ "Unknown"
)) 

victoria_merged_filter$ethnicity <- factor(victoria_merged_filter$ethnicity, c("Middle Eastern", "Latin American", "Aboriginal", "Asian", "Caucasian", "Unknown"))
tabyl(victoria_merged_filter$ethnicity)
```

## Ethnicity and Gender Plot
```{r}
ethnicity_plot <- ggplot (data = victoria_merged_filter, aes(ethnicity)) + 
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Ethnicity and Gender ", 
          x = "Ethnicity ", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=45, hjust=1))
plot(ethnicity_plot)
```

## Ethnicity grouped by gender
```{r}
CrossTable(victoria_merged_filter$ethnicity, victoria_merged_filter$gender)
```


## Income
```{r}
tabyl(victoria_merged_filter$income)

victoria_merged_filter <- victoria_merged_filter %>% mutate(income_1 = case_when(
  income == 1 ~ "No income",
  income == 2 ~ "$1 to $9,999", 
  income == 3 ~ "$10,000 to $14,999",
  income == 4 ~ "$15,000 to $19,999", 
  income == 5 ~ "$20,000 to $29,999",
  income == 6 ~ "$30,000 to $39,999",
  income == 7 ~ "$40,000 to $49,999",
  income == 8 ~ "$50,000 to $99,999",
  income == 9 ~ "$100,000 to $149,999",
  income == 10 ~ "$150,000 to $199,999",
  income == 11 ~ "$200,000 or more",
  income == 77 ~ "I don't know/Prefer not to answer"
))

victoria_merged_filter$income_1 <- factor(victoria_merged_filter$income_1, c("No income", "$1 to $9,999", "$10,000 to $14,999", "$15,000 to $19,999", "$20,000 to $29,999", "$30,000 to $39,999", "$40,000 to $49,999","$50,000 to $99,999","$100,000 to $149,999","$150,000 to $199,999", "$200,000 or more", "I don't know/Prefer not to answer"))

tabyl(victoria_merged_filter$income_1)
summary(victoria_merged_filter$income)
```

## Income and Gender Plot
```{r}
income_plot <- ggplot (data = victoria_merged_filter, aes(income_1)) + 
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Income and Gender ", 
          x = "Income", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=45, hjust=1))
plot(income_plot)
```

## Income and Gender Table
```{r}
CrossTable(victoria_merged_filter$income_1, victoria_merged_filter$gender)
```

## Income needs
```{r}
tabyl(victoria_merged_filter$income_needs)

victoria_merged_filter <- victoria_merged_filter %>% mutate(income_satisfy = case_when(
  income_needs == 1 ~ "Very well",
  income_needs == 2 ~ "Well", 
  income_needs == 3 ~ "Not so well",
  income_needs == 4 ~ "Not at all", 
  income_needs == 77 ~ "I don't know/Prefer not to answer"
))

tabyl(victoria_merged_filter$income_satisfy)
```

## Perceived Income and Gender Plot
```{r}
perceived_income_plot <- ggplot (data = victoria_merged_filter, aes(income_satisfy)) + 
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Income Satisfy Needs and Gender ", 
          x = "Income Satisfaction", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=45, hjust=1))
plot(perceived_income_plot)
```

## Bicycle Ownership Adults
```{r}
tabyl(victoria_merged_filter$transp_bikes_adults)

bicycle_ownership_adults_plot <- ggplot (data = victoria_merged_filter, aes(transp_bikes_adults)) + 
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Adult Bicycle Ownership and Gender ", 
          x = "Number of Bicycles", 
          y = "Number of Participants (n)") 
plot(bicycle_ownership_adults_plot)
```

## Bicycle Ownership Kids
```{r}
tabyl(victoria_merged_filter$transp_bikes_kids)

bicycle_ownership_kids_plot <- ggplot (data = victoria_merged_filter, aes(transp_bikes_kids)) +
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Kid Bicycle Ownership and Gender ", 
          x = "Number of Bicycles", 
          y = "Number of Participants (n)") 
plot(bicycle_ownership_kids_plot)
```

## Bicycle Facility Preference - Path 
```{r}
tabyl(victoria_merged_filter$bike_comf_a)

victoria_merged_filter <- victoria_merged_filter %>% mutate(path_comf = case_when(
  bike_comf_a == 1 ~ "Very uncomfortable",
  bike_comf_a == 2 ~ "Somewhat uncomfortable", 
  bike_comf_a == 3 ~ "Somewhat comfortable",
  bike_comf_a == 4 ~ "Very comfortable"
))

victoria_merged_filter$path_comf <- factor(victoria_merged_filter$path_comf, c("Very uncomfortable", "Somewhat comfortable", "Very comfortable"))

tabyl(victoria_merged_filter$path_comf)
```

## Bicycle Facility Preference - Path - Plot
```{r}
path_comfortable_plot <- ggplot (data = victoria_merged_filter, aes(path_comf)) +
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Preference for Bicycle Paths and Gender ", 
          x = "Level of Preference", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=45, hjust=1))
plot(path_comfortable_plot)
CrossTable(victoria_merged_filter$path_comf, victoria_merged_filter$gender)
```

## Bicycle Facility Preference - Residential street 
```{r}
tabyl(victoria_merged_filter$bike_comf_b)

victoria_merged_filter <- victoria_merged_filter %>% mutate(residential_street_comf = case_when(
  bike_comf_b == 1 ~ "Very uncomfortable",
  bike_comf_b == 2 ~ "Somewhat uncomfortable", 
  bike_comf_b == 3 ~ "Somewhat comfortable",
  bike_comf_b == 4 ~ "Very comfortable"
))

victoria_merged_filter$residential_street_comf <- factor(victoria_merged_filter$residential_street_comf, c("Very uncomfortable", "Somewhat uncomfortable", "Somewhat comfortable", "Very comfortable"))
tabyl(victoria_merged_filter$residential_street_comf)
CrossTable(victoria_merged_filter$residential_street_comf, victoria_merged_filter$gender)
```

## Bicycle Facility Preference - Residental Street - Plot
```{r}
residential_street_comfortable_plot <- ggplot (data = victoria_merged_filter, aes(residential_street_comf)) +
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Preference for Residential Street and Gender ", 
          x = "Level of Preference", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=45, hjust=1))
plot(residential_street_comfortable_plot)
```

## Bicycle Facility Preference - Residential street with traffic calming measures
```{r}
tabyl(victoria_merged_filter$bike_comf_c)

victoria_merged_filter <- victoria_merged_filter %>% mutate(res_street_traffic_calming_comf = case_when(
  bike_comf_c == 1 ~ "Very uncomfortable",
  bike_comf_c == 2 ~ "Somewhat uncomfortable", 
  bike_comf_c == 3 ~ "Somewhat comfortable",
  bike_comf_c == 4 ~ "Very comfortable",
  bike_comf_c == 77 ~ "I don't know/Prefer not to answer"
))

victoria_merged_filter$res_street_traffic_calming_comf <- factor(victoria_merged_filter$res_street_traffic_calming_comf, c( "Very uncomfortable", "Somewhat uncomfortable", "Somewhat comfortable", "Very comfortable", "I don't know/Prefer not to answer"))
tabyl(victoria_merged_filter$res_street_traffic_calming_comf)
CrossTable(victoria_merged_filter$res_street_traffic_calming_comf, victoria_merged_filter$gender)
```

## Bicycle Facility Preference - Residental Street with traffic calming - Plot
```{r}
res_street_traffic_calming_comfortable_plot <- ggplot (data = victoria_merged_filter, aes(res_street_traffic_calming_comf)) +
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Preference for Residential Street with Traffic Calming and Gender", 
          x = "Level of Preference", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=45, hjust=1))
plot(res_street_traffic_calming_comfortable_plot)
```

## Bicycle Facility Preference - Major Street with no bike lane 
```{r}
tabyl(victoria_merged_filter$bike_comf_d)

victoria_merged_filter <- victoria_merged_filter %>% mutate(major_street_no_bike_lane = case_when(
  bike_comf_d == 1 ~ "Very uncomfortable",
  bike_comf_d == 2 ~ "Somewhat uncomfortable", 
  bike_comf_d == 3 ~ "Somewhat comfortable",
  bike_comf_d == 4 ~ "Very comfortable"
))

victoria_merged_filter$major_street_no_bike_lane <- factor(victoria_merged_filter$major_street_no_bike_lane, c("Very uncomfortable", "Somewhat uncomfortable", "Somewhat comfortable", "Very comfortable"))
tabyl(victoria_merged_filter$major_street_no_bike_lane)
CrossTable(victoria_merged_filter$major_street_no_bike_lane, victoria_merged_filter$gender)
```

## Bicycle Facility Preference - Major street with no bike lane - Plot
```{r}
major_street_no_bike_lane_plot <- ggplot (data = victoria_merged_filter, aes(major_street_no_bike_lane)) +
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Preference for Major Street with No Bike Lane and Gender ", 
          x = "Level of Preference", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=45, hjust=1))
plot(major_street_no_bike_lane_plot)
```

## Bicycle Facility Preference - Major Street with bike lane 
```{r}
tabyl(victoria_merged_filter$bike_comf_e)

victoria_merged_filter <- victoria_merged_filter %>% mutate(major_street_bike_lane = case_when(
  bike_comf_e == 1 ~ "Very uncomfortable",
  bike_comf_e == 2 ~ "Somewhat uncomfortable", 
  bike_comf_e == 3 ~ "Somewhat comfortable",
  bike_comf_e == 4 ~ "Very comfortable"
))

victoria_merged_filter$major_street_bike_lane <- factor(victoria_merged_filter$major_street_bike_lane, c("Very uncomfortable", "Somewhat uncomfortable", "Somewhat comfortable", "Very comfortable"))
tabyl(victoria_merged_filter$major_street_bike_lane)
CrossTable(victoria_merged_filter$major_street_bike_lane, victoria_merged_filter$gender)
```

## Bicycle Facility Preference - Major street with bike lane - Plot
```{r}
major_street_bike_lane_plot <- ggplot (data = victoria_merged_filter, aes(major_street_bike_lane)) +
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Preference for Major Street with Bike Lane and Gender ", 
          x = "Level of Preference", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=45, hjust=1))
plot(major_street_bike_lane_plot)
```

## Bicycle Facility Preference - Major Street with separated bike lane 
```{r}
tabyl(victoria_merged_filter$bike_comf_f)

victoria_merged_filter <- victoria_merged_filter %>% mutate(major_street_separated_bike_lane = case_when(
  bike_comf_f == 1 ~ "Very uncomfortable",
  bike_comf_f == 2 ~ "Somewhat uncomfortable", 
  bike_comf_f == 3 ~ "Somewhat comfortable",
  bike_comf_f == 4 ~ "Very comfortable",
  bike_comf_f == 77 ~ "I don't know/Prefer not to answer"
))

victoria_merged_filter$major_street_separated_bike_lane <- factor(victoria_merged_filter$major_street_separated_bike_lane, c( "Very uncomfortable", "Somewhat uncomfortable", "Somewhat comfortable", "Very comfortable", "I don't know/Prefer not to answer"))
tabyl(victoria_merged_filter$major_street_separated_bike_lane)
CrossTable(victoria_merged_filter$major_street_separated_bike_lane, victoria_merged_filter$gender)
```

## Bicycle Facility Preference - Major street with separated bike lane - Plot
```{r}
major_street_separated_bike_lane_plot <- ggplot (data = victoria_merged_filter, aes(major_street_separated_bike_lane)) +
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "Preference for Major Street with Separated Bike Lane and Gender ", 
          x = "Level of Preference", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=45, hjust=1))
plot(major_street_separated_bike_lane_plot)
```

### AAA Familiarity 
```{r}
tabyl(victoria_merged_filter$aaa_familiarity)

victoria_merged_filter <- victoria_merged_filter %>% mutate(aaa_familiarity_1 = case_when(
  aaa_familiarity == 1 ~ "Yes",
  aaa_familiarity == 2 ~ "No"
))

tabyl(victoria_merged_filter$aaa_familiarity_1)
```

## AAA Familiarity - Plot
```{r}
aaa_familiarity_plot <- ggplot (data = victoria_merged_filter, aes(aaa_familiarity_1)) +
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "All Ages and Abilities Cycling Network Familiarity ", 
          x = "Familiar with AAA", 
          y = "Number of Participants (n)")
plot(aaa_familiarity_plot)
```

## AAA Good idea

```{r}
tabyl(victoria_merged_filter$aaa_idea)

victoria_merged_filter <- victoria_merged_filter %>% mutate(aaa_idea_1 = case_when(
  aaa_idea == 1 ~ "Very good idea",
  aaa_idea == 2 ~ "Somewhat good idea",
  aaa_idea == 3 ~ "Somewhat bad idea",
  aaa_idea == 4 ~ "Very bad idea",
  aaa_idea == 77 ~ "I don't know"
))

victoria_merged_filter$aaa_idea_1 <- factor(victoria_merged_filter$aaa_idea_1, c("I don't know", "Very bad idea", "Somewhat bad idea", "Somewhat good idea", "Very good idea"))
tabyl(victoria_merged_filter$aaa_idea_1)
```

## AAA Familiarity - Plot
```{r}
aaa_idea_1_plot <- ggplot (data = victoria_merged_filter, aes(aaa_idea_1)) +
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "All Ages and Abilities Cycling Network Idea ", 
          x = "Preference for AAA", 
          y = "Number of Participants (n)") + theme(axis.text.x = element_text(angle=45, hjust=1))
plot(aaa_idea_1_plot)
```

## AAA Cycle More
```{r}
tabyl(victoria_merged_filter$aaa_bike_more)

victoria_merged_filter <- victoria_merged_filter %>% mutate(aaa_bike_more_1 = case_when(
  aaa_bike_more == 1 ~ "Yes",
  aaa_bike_more == 2 ~ "No"
))

tabyl(victoria_merged_filter$aaa_bike_more_1)
```

## AAA Bike More - Plot
```{r}
aaa_bike_more_1_plot <- ggplot (data = victoria_merged_filter, aes(aaa_bike_more_1)) +
    geom_bar(aes(fill = gender), position = "dodge") + 
      labs(title = "All Ages and Abilities Cycling Network - Bicycle more ", 
          x = "Bicycle more",
          y = "Number of Participants (n)")
plot(aaa_bike_more_1_plot)
```

## Physical Activity - Cycling 
```{r}
tabyl(victoria_merged_filter$travel_bike)
victoria_merged_filter <- mutate(victoria_merged_filter, "Cycling_formula" = 6 * travel_bike_freq * travel_bike)
victoria_merged_filter <- mutate(victoria_merged_filter, "Walking_formula" = 3.3 * travel_walk_freq * travel_walk)
victoria_merged_filter <- mutate(victoria_merged_filter, "Total_transport_formula" = Cycling_formula + Walking_formula)
```

## Plotting PA
```{r}
PA_cycling_plot <- ggplot (data = victoria_merged_filter, aes(Cycling_formula)) + 
    geom_density(aes(fill = gender), position = "dodge", alpha = 0.5) + 
      labs(title = "Cycling for Transport Physical Activity", 
          x = "Cycling MET Minutes of Physical Activity", 
          y = "Percent of Participants")
plot(PA_cycling_plot)
```

## Adding normal distribution to PA plot 
```{r}
victoria_merged_filter$Cycling_formula <- as.numeric(victoria_merged_filter$Cycling_formula)
PA_cycling_normal_plot  <- PA_cycling_plot +
  stat_function(fun = dnorm, args = list(mean = mean(victoria_merged_filter$Cycling_formula, na.rm = TRUE), sd =sd(victoria_merged_filter$Cycling_formula, na.rm = TRUE)), color = "red", size = 1)
plot(PA_cycling_normal_plot)
```

## Descriptive Stats for Cycling PA
```{r}
summary(victoria_merged_filter$Cycling_formula)
describeBy(victoria_merged_filter$Cycling_formula)
describeBy(victoria_merged_filter$Cycling_formula, victoria_merged_filter$gender)

tabyl(victoria_merged_filter$Cycling_formula)
```

## Filtering out other in gender category 

```{r}
victoria_merged_filter <- victoria_merged_filter %>% mutate(gender_new = case_when(
  gender == "Female" ~ "Female",
  gender == "Male" ~ "Male"
)) 
tabyl(victoria_merged_filter$gender_new)
```

## Regression - Regression Model 1 with just PA and Gender 
```{r}
gender_regression_1 <- lm(Cycling_formula ~ gender,  data = victoria_merged_filter)

summary(gender_regression_1)
lm.beta(gender_regression_1) ##This isn't working. 
confint(gender_regression_1)
plot(gender_regression_1)
```

## Write CSV
```{r}
write.csv(victoria_merged_filter, file = "victoria_merged_filter.csv")
```


## Spearman's Correlation Coefficient - Gender
```{r}
cor.test(victoria_merged_filter$support_index, victoria_merged_filter$gender_number, alternative = "less", method = "spearman")
#not significant - no correlation (4%)
```


## Spearman's Correlation Coefficient - Age
```{r}
cor.test(victoria_merged_filter$support_index, victoria_merged_filter$age_calculated, alternative = "less", method = "spearman")
#not significant - no correlation (-3.6%)
```

## Spearman's Correlation Coefficient - Health Status
```{r}
cor.test(victoria_merged_filter$support_index, victoria_merged_filter$sf1, alternative = "less", method = "spearman")
# not significant - no correlation (-.6%)
```

## Spearman's Correlation Coefficient - Income 
```{r}
cor.test(victoria_merged_filter$support_index, victoria_merged_filter$income, alternative = "less", method = "spearman")
# not significant - no correlation (9.6%)
```

## Spearman's Correlation Coefficient - Marital status
```{r}
cor.test(victoria_merged_filter$support_index, victoria_merged_filter$marital_status, alternative = "less", method = "spearman")
# not significant - no correlation (5.7%)
```

## Spearman's Correlation Coefficient - Ethnicity
```{r}
cor.test(victoria_merged_filter$support_index, victoria_merged_filter$ethnicity_number, alternative = "less", method = "spearman")
# not significant - no correlation (.04%)
```

## Spearman's Correlation Coefficient - Cycling MET-minutes of PA
```{r}
cor.test(victoria_merged_filter$support_index, victoria_merged_filter$Cycling_formula, alternative = "less", method = "spearman")
# significant -12%
```

## Spearman's Correlation Coefficient - Cycling MET-minutes of PA and comfortable on separated
```{r}
cor.test(victoria_merged_filter$separated_bike_lane, victoria_merged_filter$Cycling_formula, alternative = "less", method = "spearman")
# significant -14%
```
## Scatterplot 

## Scatterplot analyzing support index and age 
```{r}
scatter_support_age <- ggplot(victoria_merged_filter, aes(support_index, age_calculated))

scatter_support_age_1 <- scatter_support_age +
                           geom_point() +
                             labs(title = "Scatterplot of Age and Support Index for AAA",
                               x = "Support Index for AAA", 
                                y = "Age")
plot(scatter_support_age_1)
```
