---
title: "regression_models"
author: "Melissa Tobin"
date: "19/06/2019"
output:   
  html_document:
        keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics = FALSE, ind = 1)

OS <- Sys.info()
if (OS["sysname"] == "Windows") {
  path <-
    "Z:/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis Results/INTERACT thesis Analysis"
} else {
  path <-
    "/Volumes/hkr-storage/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis Results/INTERACT thesis Analysis"
}
setwd(path)
```

## Loading Packages
```{r}
library(lmtest)
library(tidyverse)
library(ggplot2)
library(haven)
library(janitor)
library(pastecs)
library(psych)
library(car)
library(Hmisc)
library(ggm)
library(polycor)
library(tableone)
library(forcats)
library(gmodels)
library(QuantPsyc)
library(KernSmooth)
library(raster)
library(sp)
library(sf)
library(lubridate)
library(anytime)
library(stringr)
library(stringi)
library(finalfit)
library(data.table)
install.packages("devtools")
devtools::install_github("cardiomoon/ggiraphExtra")
require(ggiraph)
require(ggiraphExtra)
require(plyr)
```

## Reading in data
```{r}
victoria_small_merged_1 <- fread("victoria_small_merged_1.csv")

power_victoria_merged_updated <- fread("power_victoria_merged_updated.csv") #big file with all summary counts
table_of_power_merged_2 <- fread("table_of_power_merged_2.csv")
summary_power_victoria_merged_updated <- fread("summary_power_victoria_merged_updated.csv") #summary table with summarized PA
```

## Variables
```{r}
power_victoria_merged_updated$income_2 <- factor(power_victoria_merged_updated$income_2, c("$49,000 or less", "$50,000 to $99,999", "$100,000 to $149,999", "$150,000 or more", "I don't know/Prefer not to answer")) 

tabyl(power_victoria_merged_updated$income_2)

power_victoria_merged_filtered <- power_victoria_merged_updated %>% filter(gender_check == 1)

write_csv(power_victoria_merged_filtered, "power_victoria_merged_filtered.csv")

tabyl(power_victoria_merged_filtered$summary_count)

summary_power_victoria_merged_filtered <- summary_power_victoria_merged_updated %>% filter(gender_check == 1)
write_csv(summary_power_victoria_merged_filtered, "summary_power_victoria_merged_filtered.csv")
```

## Traditional regression using lm function for survey data + plot
```{r}
regression_1 <- lm(total_pa_met_formula ~ percent, data = victoria_small_merged_1)

summary(regression_1)
lm.beta(regression_1) ##This isn't working. 
confint(regression_1)
#plot(regression_1

ggPredict(regression_1, se = TRUE, interactive = TRUE)
```

## Regression Model with Survey Data - Final Fit Package
```{r}
victoria_small_merged_1 <- victoria_small_merged_1 %>% 
                              mutate_at(vars(income_2, age_categories, ethnicity_updated), as.factor)

explanatory = c("percent", "gender_updated", "age_categories", "ethnicity_updated", "income_2", "mean_temp_date", "total_precip_date")
dependent = "total_pa_met_formula"
victoria_small_merged_1 %>% finalfit(dependent, explanatory) -> t1
knitr::kable(t1, row.names = FALSE, align = c("l", "l", "r", "r", "r")) 
```

## Regression Model (lm) with self-report PA and all predictors 
```{r}
victoria_small_merged_1$income_2 <- factor(victoria_small_merged_1$income_2, c("$49,000 or less", "$50,000 to $99,999", "$100,000 to $149,999", "$150,000 or more", "I don't know/Prefer not to answer")) 

tabyl(victoria_small_merged_1$income_2)
lm_1 <- lm(total_pa_met_formula ~ percent + gender_updated + age_categories + ethnicity_updated + income_2 + mean_temp_date + total_precip_date, data = victoria_small_merged_1)
summary(lm_1)
confint(lm_1)

lm_1_plot <- ggplot(victoria_small_merged_1, aes(y = total_pa_met_formula, x = percent)) + 
               geom_point() +
                geom_smooth(method = "lm") +         
                  labs(title = "Exposure to Pandora protected cycling lane and Physical Activity (Self-Report)",
                  x = "Percent Exposure",
                 y = "Total MET-Minutes of Physical Activity per week")
plot(lm_1_plot)  
##This plot works but only has exposure and outcome. I don't know how to include all predictor variables
```

## Regression Model with summary accelerometer data
```{r}
summary_power_victoria_merged_updated <- summary_power_victoria_merged_updated %>% 
                              mutate_at(vars(income_2, age_categories, ethnicity_updated), as.factor)
explanatory = c("percent", "gender_updated", "age_categories", "ethnicity_updated", "income_2", "mean_temp_date", "total_precip_date")
dependent = "total_pa"
summary_power_victoria_merged_updated %>% finalfit(dependent, explanatory) -> t2
knitr::kable(t2, row.names = FALSE, align = c("l", "l", "r", "r", "r")) 
```

## Simple regression plot for summary accelerometer data
```{r}
ggplot(summary_power_victoria_merged_updated, aes(y = total_pa, x = percent)) + 
  geom_point() +
  geom_smooth(method = "lm")
```

## Regression Model with summary_counts as outcome variable - from accelerometer data
```{r}
power_victoria_merged_filtered <- power_victoria_merged_filtered %>% 
                              mutate_at(vars(income_2, age_categories, ethnicity_updated), as.factor)
explanatory = c("percent", "doy_1", "gender_updated", "age_categories", "ethnicity_updated", "income_2", "mean_temp_date", "total_precip_date")
dependent = "summary_count"
power_victoria_merged_filtered %>% finalfit(dependent, explanatory) -> t3
knitr::kable(t3, row.names = FALSE, align = c("l", "l", "r", "r", "r")) 
```

## Making plots for regression - accelerometer data
```{r}
pa_regression_1 <- lm(summary_count ~ percent,  data = power_victoria_merged_filtered)

summary(pa_regression_1)
lm.beta(pa_regression_1) ##This isn't working. 
confint(pa_regression_1)

ggplot(power_victoria_merged_filtered, aes(y = summary_count, x = percent)) + 
  geom_point() +
  geom_smooth(method = "lm")
```

## Analyzing the regression data more closely 
```{r}
summary(power_victoria_merged_filtered$summary_count)
sd(power_victoria_merged_filtered$summary_count, na.rm = TRUE)
describeBy(power_victoria_merged_filtered$summary_count)
summary_counts_plot <- ggplot(power_victoria_merged_filtered) + 
                          geom_histogram(aes(summary_count), bins = 50) +
                            labs(title = "Accelerometer Activity Counts",
                             x = "Activity Count",
                             y = "Number of Counts (n)")
plot(summary_counts_plot)
```

## Negative binomial regression with just percent and summary count
```{r}
nb_regression_1 <- glm.nb(summary_count ~ percent, data = power_victoria_merged_filtered)
summary(nb_regression_1)

power_victoria_merged <- fread("power_victoria_merged.csv")
nb_regression_old <- glm.nb(summary_count ~ percent, data = power_victoria_merged)
summary(nb_regression_old)
```

## Negative binomial regression with all predictors
```{r}
nb_regression_2 <- glm.nb(summary_count ~ percent + gender_updated + age_categories + ethnicity_updated + income_2 + mean_temp_date + total_precip_date, data = power_victoria_merged_filtered)
summary(nb_regression_2)
```

## Checking assumptions for negative binomial filtered model
```{r}
poisson_regression <- glm(summary_count ~ percent + gender_updated + age_categories + ethnicity_updated + income_2 + mean_temp_date + total_precip_date, family = "poisson", data = power_victoria_merged_filtered)
summary(poisson_regression)

pchisq(2 * (logLik(nb_regression_2) - logLik(poisson_regression)), df = 1, lower.tail = FALSE)
```

## Confidence interavls
```{r}
est <- cbind(Estimate = coef(nb_regression_2), confint(nb_regression_2))
incident_rate_ratios <- exp(est)
```

## Recoding to numeric for plotting 
```{r}
tabyl(power_victoria_merged_filtered$income_2)

power_victoria_merged_filtered <- power_victoria_merged_filtered %>% mutate(ethnicity_1 = case_when(
  ethnicity_updated == "Caucasian" ~ 1,
  ethnicity_updated == "Racialized Group" ~ 2
))

power_victoria_merged_filtered <- power_victoria_merged_filtered %>% mutate(gender_1 = case_when(
  gender_updated == "Men" ~ 1,
  gender_updated == "Women" ~ 2
))

power_victoria_merged_filtered <- power_victoria_merged_filtered %>% mutate(age_categories_1 = case_when(
  age_categories == "20-29" ~ 1,
  age_categories == "30-39" ~ 2,
  age_categories == "40-49" ~ 3,
  age_categories == "50-59" ~ 4,
  age_categories == "60+" ~ 5,
))

power_victoria_merged_filtered <- power_victoria_merged_filtered %>% mutate(income_3 = case_when(
  income_2 == "$49,000 or less" ~ 1,
  income_2 == "$50,000 to $99,999" ~ 2,
  income_2 == "$100,000 to $150,000" ~ 3,
  income_2 == "$150,000 or more" ~ 4,
  income_2 == "I don't know/Prefer not to answer" ~ 5,
))

```

##Plotting Regression
```{r}
ggplot(power_victoria_merged_filtered, aes(y = 
      summary_count, x = percent + ethnicity_1 + gender_1 + age_categories_1 + income_3 + mean_temp_date +
        total_precip_date)) + 
          geom_point() +
            geom_smooth(method = "glm.nb") +
               labs(title = "Exposure to Pandora protected cycling lane and Physical Activity (Activity Counts)",
                 x = "Predictor Variables (Exposure, Ethnicity, Gender, Age, Income, Mean temperature, Total Precipitation (mm)",
                 y = "Activity Counts")
```

```{r}
ggplot(power_victoria_merged_filtered, aes(y = 
      summary_count, x = percent)) + 
          geom_point() +
            geom_smooth(method = "glm.nb") +
               labs(title = "Exposure to Pandora protected cycling lane and Physical Activity (Activity Counts)",
                 x = "Exposure to Pandora (Percentage of total points",
                 y = "Activity Counts")
```

## Negative binomial regression with filtered summary count data
```{r}
summary_count <- tabyl(power_victoria_merged_filtered$summary_count)
tail(summary_count$`power_victoria_merged_filtered$summary_count`)

filtered_power <- power_victoria_merged_filtered %>% filter(summary_count <= 10000)

filtered_counts_plot <- ggplot(filtered_power) + 
                          geom_density(aes(summary_count), bins = 50)

plot(filtered_counts_plot)

nb_regression_filtered <- glm.nb(summary_count ~ percent, data = filtered_power)
summary(nb_regression_filtered)

nb_regression_2_filtered <- glm.nb(summary_count ~ percent + gender_updated + age_categories + ethnicity_updated + income_2 + mean_temp_date + total_precip_date, data = filtered_power)
summary(nb_regression_2_filtered)

summary(filtered_power$summary_count)
sd(filtered_power$summary_count)
```

## Zero-inflated Negative Binomial Regression
```{r}
library(MASS)
install.packages("pscl")
library(pscl)
library(boot)
model_1 <- zeroinfl(summary_count ~ percent, data = power_victoria_merged_filtered, dist = "negbin", EM = TRUE)
```

