---
title: "regression_models_updated"
author: "Melissa Tobin"
date: "02/07/2019"
output: 
  html_document:
        keep_md: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics = FALSE, ind = 1)

OS <- Sys.info()
if (OS["sysname"] == "Windows") {
  path <-
    "Z:/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis Results/INTERACT thesis Analysis"
} else {
  path <-
    "/Volumes/hkr-storage/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis Results/INTERACT thesis Analysis"
}
setwd(path)
```

## Loading Packages
```{r}
library(lmtest)
library(tidyverse)
library(ggplot2)
library(haven)
library(janitor)
library(pastecs)
library(psych)
library(car)
library(Hmisc)
library(ggm)
library(polycor)
library(tableone)
library(forcats)
library(gmodels)
library(QuantPsyc)
library(KernSmooth)
library(raster)
library(sp)
library(sf)
library(lubridate)
library(anytime)
library(stringr)
library(stringi)
library(finalfit)
library(data.table)
```

## Reading in data
```{r}
power_victoria_filtered <- fread("power_victoria_filtered.csv")

victoria_exposure_filtered <- read_csv("victoria_exposure_filtered.csv") 
```

## Multiple Regression with all predictors - updated with filtered exposure data
```{r}
victoria_exposure_filtered$income_2 <- factor(victoria_exposure_filtered$income_2, c("$49,000 or less", "$50,000 to $99,999", "$100,000 to $149,999", "$150,000 or more", "I don't know/Prefer not to answer")) 

lm_1 <- lm(total_pa_met_formula ~ percent + gender_updated + age_categories + ethnicity_updated + income_2 + mean_temp_date + total_precip_date, data = victoria_exposure_filtered)
summary(lm_1)
confint(lm_1)
```

## Plotting exposure and outcome
```{r}
lm_1_plot <- ggplot(victoria_exposure_filtered, aes(y = total_pa_met_formula, x = percent)) + 
               geom_point() +
                geom_smooth(method = "lm") +         
                  labs(title = "Exposure to Pandora protected cycling lane and Physical Activity (Self-Report)",
                  x = "Percent Exposure",
                 y = "Total MET-Minutes of Physical Activity per week")
plot(lm_1_plot)  
##This plot works but only has exposure and outcome. I don't know how to include all predictor variables
```

## Checking assumptions for linear regression
```{r}
victoria_exposure_filtered$residuals <- resid(lm_1, na.rm = TRUE)
victoria_exposure_filtered$standardized.residuals <- rstandard(lm_1)
victoria_exposure_filtered$studentized.residuals <- rstudent(lm_1) 
victoria_exposure_filtered$cooks.distance <- cooks.distance(lm_1) 

durbinWatsonTest(lm_1) #checking for independence
vif(lm_1)
1/vif(lm_1)
mean(vif(lm_1))
plot(lm_1)
```

## Plotting Residuals
```{r}
residual_plot <- ggplot(victoria_exposure_filtered, aes(standardized.residuals)) + geom_density() +
                  geom_vline(xintercept = 2, colour = "red") + geom_vline(xintercept = -2, colour= "red") +
                    labs(title = "Standardized Residuals Plot", x = "Standarized Residuals",
                      y = "Density (% of Participants)")

plot(residual_plot)

tabyl(victoria_exposure_filtered$standardized.residuals)
```

## Cook's Plot
```{r}
cooks_plot <- ggplot(victoria_exposure_filtered, aes(cooks.distance)) +
                geom_density() +
                geom_vline(xintercept = 1, colour = "red") +
                labs(title = "Cooks Plot", 
                     x = "Cooks Distance",
                     y = "Density (% of Participants")
plot(cooks_plot)
```

## Negative binomial regression with updated filtered exposure data - exposre and outcome
```{r}
nb_regression_3 <- glm.nb(summary_count ~ percent, data = power_victoria_filtered)
summary(nb_regression_3)
```

## Negative binomial regression with all predictors - updated with filtered exposure data
```{r}
power_victoria_filtered$income_2 <- factor(power_victoria_filtered$income_2, c("$49,000 or less", "$50,000 to $99,999", "$100,000 to $149,999", "$150,000 or more", "I don't know/Prefer not to answer")) 

nb_regression_4 <- glm.nb(summary_count ~ percent + gender_updated + age_categories + ethnicity_updated + income_2 + mean_temp_date + total_precip_date, data = power_victoria_filtered)
summary(nb_regression_4)
confint(nb_regression_4)
```

## Checking assumptions for negative binomial filtered model
```{r}
poisson_regression <- glm(summary_count ~ percent + gender_updated + age_categories + ethnicity_updated + income_2 + mean_temp_date + total_precip_date, family = "poisson", data = power_victoria_filtered)
summary(poisson_regression)

pchisq(2 * (logLik(nb_regression_4) - logLik(poisson_regression)), df = 1, lower.tail = FALSE)
```

## Confidence interavls
```{r}
est <- cbind(Estimate = coef(nb_regression_4), confint(nb_regression_4))
incident_rate_ratios <- exp(est)
```

## Recoding to numeric for plotting 
```{r}
power_victoria_filtered <- power_victoria_filtered %>% mutate(ethnicity_1 = case_when(
  ethnicity_updated == "Caucasian" ~ 1,
  ethnicity_updated == "Racialized Group" ~ 2
))

power_victoria_filtered <- power_victoria_filtered %>% mutate(gender_1 = case_when(
  gender_updated == "Men" ~ 1,
  gender_updated == "Women" ~ 2
))

power_victoria_filtered <- power_victoria_filtered %>% mutate(age_categories_1 = case_when(
  age_categories == "20-29" ~ 1,
  age_categories == "30-39" ~ 2,
  age_categories == "40-49" ~ 3,
  age_categories == "50-59" ~ 4,
  age_categories == "60+" ~ 5,
))

power_victoria_filtered <- power_victoria_filtered %>% mutate(income_3 = case_when(
  income_2 == "$49,000 or less" ~ 1,
  income_2 == "$50,000 to $99,999" ~ 2,
  income_2 == "$100,000 to $150,000" ~ 3,
  income_2 == "$150,000 or more" ~ 4,
  income_2 == "I don't know/Prefer not to answer" ~ 5,
))
```

## Plotting Regression with exposure and outcome 
```{r}
ggplot(power_victoria_filtered, aes(y = 
      summary_count, x = percent)) + 
          geom_point() +
            geom_smooth(method = "glm.nb") +
               labs(title = "Exposure to Pandora protected cycling lane and Physical Activity (Activity Counts)",
                 x = "Exposure to Pandora (Percentage of total points",
                 y = "Activity Counts")
```

##Plotting Regression with all predictors
```{r}
ggplot(power_victoria_filtered, aes(y = 
      summary_count, x = percent + ethnicity_1 + gender_1 + age_categories_1 + income_3 + mean_temp_date +
        total_precip_date)) + 
          geom_point() +
            geom_smooth(method = "glm.nb") +
               labs(title = "Exposure to Pandora protected cycling lane and Physical Activity (Activity Counts)",
                 x = "Predictor Variables (Exposure, Ethnicity, Gender, Age, Income, Mean temperature, Total Precipitation (mm)",
                 y = "Activity Counts")
```



